Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\begin{tikzpicture}
	\begin{axis}[axis lines=center,
				axis on top,
				set layers=default,
				xrange=-5:5,
				yrange=-2:2,
				unit vector ratio=1 1 1, scale=1.5,
				view={45}{40},
				]
		\addplot3[	surf,] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

		\addplot3[	surf,	] 
		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
		};

		\addplot3[	surf,	] 
		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
		};

			\addplot3[	surf,	] 
		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
		};

>>>>

\begin{tikzpicture}
	\begin{axis}[	axis on top,
				set layers=default,
				xrange=-5:5,
				yrange=-2:2,
				unit vector ratio=1 1 1, scale=1.5,
				view={60}{50},
				]
		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
		};

		\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
		};

			\addplot3[fill=blue,opacity=0.1, fill opacity=0.4	] 
		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
		};

\begin{tikzpicture}
	\begin{axis}[	axis on top,
		set layers=default,
		xrange=-5:5,
		yrange=-2:2,
		unit vector ratio=1 1 1, scale=1.5,
		view={35}{14},
		]
		\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates {
			(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4] 
		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
		};

		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
		};

		\addplot3[	fill=blue,opacity=0.1, fill opacity=0.4	] 
		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
		};
